\chapter{Introduction}

The design process usually starts with rough doodles and sketches to create a basic visual representation of the solution to a problem.
The processes from this conceptual stage to more detailed specifications has often been segmented between incompatible physical and virtual representations.
Unfortunately, the answers to many important questions about the design are made during the conceptual stage without all of the information the designer needs, because getting this information requires a digital representation of the work that is currently too difficult to create during the rapid pace of the conceptual stage.
Historically, there have been constraints to digitizing the conceptual design stage: displays were too small and the forced use of the mouse and keyboard were far more difficult to work with that the traditional methods of pen and paper.
However, with the advent of large touch panel displays (e.g., the 55-inch Surface Hub Display), it is possible to implement a digital system that closely mimics a traditional conceptual design process.

In this work, we implement a sketching interface that allows the user to create drawings in three dimensions.
The interface is capable of using modern input devices to approximate the act of real world sketching as closely as possible.
These devices include a display capable of multi-touch input, as well as a special electronic pen which relays extra information
not sent through regular touch input.
For the sketch itself, we implement a spline-based data structure in order to store high quality, three dimensional strokes, that can be zoomed in without loss in quality.
We also implement a three-dimensional line rendering library, as native line rendering implementations are poor quality.

When creating a three-dimensional model, much of the work is done on a computer using Computer-Aided Design (CAD) software specifically designed for the unique application.
For example, in the architecture profession, Rhino and Revit are used to create building models.
In the animation industry, Maya, Blender, and 3DSMax are used to create character models and complex scenery.
In both cases however, the initial designs are still done using two-dimensional sketches, rough drawings not intended as the finished work.
Sketches are generally not highly detailed works, as they intend to only capture the essentials of a final design.
Through a number of rough sketches, a three-dimensional form can be implied through the representations of perspective and volume.
This two-dimensional information is then used as a reference when designing the final three-dimensional model.
Details of modern approaches to content creation on a computer are presented in Chapter 2.

In architecture, there is a push towards creating buildings that reduce energy consumption though heating, cooling, and lighting.
If an architect has a three dimensional model, it can be analyzed to predict how well it uses energy.
However, if the building has poor results, the architect can only make superficial changes to the structure of the building, since much of the design process has already been approved.
If we are able to digitize the early phase design process such that a rudimentary three-dimensional model can be made, architects can analyze their models earlier in the design process, and use this information to better design energy efficient buildings.

Sketching is an old method of expressing ideas, and has a variety of techniques associated with the practice.
Many professionals have been reluctant to use computer software, because the skills they have used and trained themselves in do not transfer to the digital medium.
In recent years, technology has advanced to where the creation of specialized user input devices can allow better emulation of traditional sketching techniques.
These devices are explored in Chapter~\ref{ch:input}.

In our interface, a user sketches through an interaction window displaying a scene.
This scene contains geometry of some form that the user can draw on.
Every time the user draws on an object, a stroke is created.
In Chapters 4 and 5, we discuss how the rough, two dimensional user input is transformed into a high-quality, three-dimensional spline curve.
This spline is rendered in real time using OpenGL.
However, the native support for displaying curves is limited, as many artifacts appear in the final curve when naively attempting to render them.
Details on the approach we use to display our curves in high quality is discussed in Chapter 6.