\begin{abstract}
The design process usually starts with rough doodles and sketches to create a basic visual representation of the solution to a problem. The processes from this conceptual stage to more detailed specifications has often been segmented between incompatible physical and virtual representations. This work explores digital 3D sketching using large touch panel displays and active pen technology for the use in the early stages of the design process. We focus on rendering high quality 3D curves in a free-form sketching environment.
\end{abstract}

\begin{biosketch}
The author was born in Manhattan, New York on August 21st, 1991. Currently, he resides in Staten Island, New York. In 2009, he started undergrad at Cornell University. After graduating with a Computer Science degree, he entered the Program of Computer Graphics the following year.
\end{biosketch}

\begin{dedication}
I dedicate this thesis to my family and friends whose support helped make this possible.
\end{dedication}

\begin{acknowledgements}
First, I would like to thank my parents, Douglas and Carolyn, my brother Michael, and my girlfriend Athena for their constant support.

I am very grateful to Professor Donald Greenberg for providing me with the opportunity to study at the Cornell Program of Computer Graphics. The knowledge, experience, and opportunities I have gained throughout the degree would not have been possible without someone as incredible as Don running the show.

I would like to thank Professor Kavita Bala for providing me with many opportunities to expand my knowledge of computer graphics. I would also like to thank her for being an advisor on my thesis committee.
\end{acknowledgements}
